---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **random iterations of fragmenting arabidopsis genome**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
#opts_chunk$set(dev = 'pdf')
library(reshape2)
library(MESS)

# source custom R functions
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/ggplot_theme.R')
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/zero_ratio_adj.R')

```

...     
Arabdiopsis genome is fragmented using a log-normal distribution with parameters derived from an assembly made using Allen et al miR159 sequence data.

1000 iterations of fragments were generated and parent filtered hasty mutant variant information is used to assign variants to made genome fragments

Data resulting 1000 iteration is used to make following boxplots

...  		

#### box plot of number of fragments, fragments with variants and fragments with more homozygous than heterozygous variants

```{r boxplot, echo=FALSE, fig.width=12, fig.height=6}
newtable <- data.frame(t(rep(NA,4)))
names(newtable) <- c("Fragment", "WithVars", "MoreHomozygous", "AUC")
dir = getwd()
dir = paste(dir, "vars_infrags", sep='/')
## read all files in a folder and store to a dataframe
filelist = list.files(dir, "^genome_")
for (i in 1:length(filelist)) {
  filename = paste(dir, filelist[i], sep='/')
  newdf <- read.delim(file=filename, header = TRUE)
  newdf$vars = newdf$numhm + newdf$numht
  newdf$vardiff = newdf$numhm - newdf$numht
  numfrags = nrow(newdf)
  selected = subset(newdf, vars > 0)
  withvars = nrow(selected)
  selected$position <- cumsum(selected$length)
  selected <- re_zero_ratio(selected, 0.5)
  auc_calc = auc(selected$position, selected$ratio)
  morehm = nrow(subset(newdf, vardiff > 0))
  newtable[i,] <- c(numfrags, withvars, morehm, auc_calc)
}

write.table(newtable, file="random_frag_contig_analysis.txt", sep="\t", row.names = FALSE)
#melted <- melt(newtable)
#ggplot(data=melted, aes(x=variable, y=value)) + geom_boxplot() + facet_grid(variable ~ ., scales="free")
par(mfrow=c(1,4))
boxplot(newtable$Fragment, xlab="num fragments", cex.lab=2.5, cex.axis=2.5)
boxplot(newtable$WithVars, xlab="frags with vars", cex.lab=2.5, cex.axis=2.5)
boxplot(newtable$MoreHomozygous, xlab="more heterozygous", cex.lab=2.5, cex.axis=2.5)
boxplot(newtable$AUC, xlab="area under curve", cex.lab=2.5, cex.axis=2.5)

```


...


...

