---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **plots of variant distribution along chromosome length**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
#opts_chunk$set(dev = 'pdf')
library(reshape2)

# source custom R functions
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/ggplot_theme.R')
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/zero_ratio_adj.R')
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/lm_eqn_plot.R')

```

...     

...  		

#### 2.5Mb-10kb grouping of whole genome

```{r 2.5Mb-10kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="2500000-per10000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 10 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(1250000), size=0.5)

```


...		

...  		

#### 2.5Mb-100kb grouping of whole genome

```{r 2.5Mb-100kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="2500000-per100000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 100 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(1250000), size=0.5)

```


...	

...  		

#### 2.5Mb-500kb grouping of whole genome

```{r 2.5Mb-500kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="2500000-per500000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 500 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(1250000), size=0.5)

```


...	


...  		

#### 5Mb-10kb grouping of whole genome

```{r 5Mb-10kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="5000000-per10000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 10 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(2500000), size=0.5)

```


...		

...  		

#### 5Mb-100kb grouping of whole genome

```{r 5Mb-100kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="5000000-per100000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 100 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(2500000), size=0.5)

```


...	

...  		

#### 5Mb-500kb grouping of whole genome

```{r 5Mb-500kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="5000000-per500000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 500 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(2500000), size=0.5)

```


...	

...  		

#### 10Mb-10kb grouping of whole genome

```{r 10Mb-10kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="10000000-per10000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 10 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(5000000), size=0.5)

```


...		

...  		

#### 10Mb-100kb grouping of whole genome

```{r 10Mb-100kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="10000000-per100000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 100 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(5000000), size=0.5)

```


...	

...  		

#### 10Mb-500kb grouping of whole genome

```{r 10Mb-500kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="10000000-per500000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 500 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(5000000), size=0.5)

```


...	

...  		

#### 25Mb-10kb grouping of whole genome

```{r 25Mb-10kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="25000000-per10000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 10 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(12500000), size=0.5)

```


...		

...  		

#### 25Mb-100kb grouping of whole genome

```{r 25Mb-100kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="25000000-per100000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 100 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(12500000), size=0.5)

```


...	

...  		

#### 25Mb-500kb grouping of whole genome

```{r 25Mb-500kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="25000000-per500000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 500 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(12500000), size=0.5)

```


...	


...  		

#### 50Mb-10kb grouping of whole genome

```{r 50Mb-10kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="50000000-per10000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 10 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(25000000), size=0.5)

```


...		

...  		

#### 50Mb-100kb grouping of whole genome

```{r 50Mb-100kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="50000000-per100000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 100 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(25000000), size=0.5)

```


...	

...  		

#### 50Mb-500kb grouping of whole genome

```{r 50Mb-500kb, echo=FALSE, fig.width=12, fig.height=6}
tenkb <- read.delim(file="50000000-per500000bp-filtered_96_1_fd2_mutant.vcf.txt", header = TRUE)
tenkb <- re_zero_ratio(tenkb, 0.01)
melted <- melt(tenkb, id.vars = "position")
ggplot(data=melted, aes(x=position, y=value)) + geom_bar(stat="identity", colour="#E69F00", fill="#E69F00") +
  facet_grid(variable ~ ., scales = "free") +
  scale_y_sqrt() + labs(y=NULL, main="genome in 500 KB fragment chunks") + mytheme +
  geom_vline(xintercept = as.numeric(25000000), size=0.5)

```


...	

