---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **fragments carrying causative sup2 mutation from random iterations of arabidopsis genome**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
#opts_chunk$set(dev = 'pdf')
library(reshape2)
library(MESS)

# source custom R functions
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/ggplot_theme.R')
source('~/git-hub-repos/shyamrallapalli/mutations_hts_noref/lib/zero_ratio_adj.R')

```

...     
Arabdiopsis genome is fragmented using a log-normal distribution with parameters derived from an assembly made using Allen et al miR159 sequence data.

867 iterations of fragments were generated and parent filtered sup2 mutant variant information is used to assign variants to made genome fragments

Data for the fragment carrying sup2 mutation from all iterations is extracted

...  		

...

##### read file with fragment ids of causatiave mutation for all iterations
##### store the data in a dataframe and write to a table

```{r analysis, include=FALSE}

frags <- read.delim(file="fragments_with_mut_ids.txt", header = TRUE)
colnames(frags) <- c("iterations", "fragment")

# create empty data frame to store information about
# mutation carrying fragments from all iterations
selected = data.frame(fragment=character(),
  length=numeric(),
  numhm=numeric(),
  numht=numeric(),
  file=character(),
  stringsAsFactors=FALSE)

## read all files in a folder and store to a dataframe
dir = getwd()
dir = paste(dir, "vars_infrags", sep='/')
filelist = list.files(dir, "^genome_")
numfiles = length(filelist)

for (i in 1:numfiles) {
  filename = paste(dir, filelist[i], sep='/')
  newdf <- read.delim(file=filename, header = TRUE, stringsAsFactors=FALSE)
  iteration = gsub("_varinfo.txt$", "", filelist[i])
  fragid = as.character(frags[which(frags$iterations == iteration),]$fragment)
  selected[i,] = c(subset(newdf, fragment==fragid), iteration)
}

# save all iteration fragment data to a file
write.table(selected, file="frags_mutation_all_iterations.txt", sep="\t", row.names = FALSE)

```

...

...


#### box plot of length fragments, homozygous, heterozygous variants and ratio

```{r boxplot, echo=FALSE, fig.width=12, fig.height=6}

selected <- re_zero_ratio(selected, 0.5)
selected$adjratio <- selected$ratio/selected$length
par(mfrow=c(1,4))
boxplot(selected$length, xlab="length", cex.lab=2.5, cex.axis=2.5)
boxplot(selected$ratio, xlab="ratio", cex.lab=2.5, cex.axis=2.5)
boxplot(selected$numhm, xlab="homozygous", cex.lab=2.5, cex.axis=2.5)
boxplot(selected$adjratio, xlab="length adj ratio", cex.lab=2.5, cex.axis=2.5)

```


...


#### ratios of fragments with causative mutation

```{r plotvars, echo=FALSE, fig.width=12, fig.height=12}

summary(selected$ratio)

```


...

...
