---
output:
  html_document:
    fig_caption: yes
    theme: spacelab
    toc: no
---
# **plots of variant distribution along chromosome length**

Load libraries and the data
```{r setup, include=FALSE}
# load the required libraries and functions
library(knitr)
library(markdown)
opts_chunk$set(dev = 'pdf')
library(ggplot2)
library(gridExtra)

## cusotom ggplot theme edits
mytheme <- theme(panel.background = element_rect(fill='white', colour='black'),
        text = element_text(size = 20, face='bold', colour='black'),
        axis.title.x = element_text(size = 19, face='bold', color='black', vjust = -1),
        axis.text = element_text(size = 17, face='bold', color='black'),
        panel.grid.major = element_line(linetype = 'dotted', colour='black'),
        panel.border = element_rect(fill=NA, linetype = "solid", colour='black'),
        plot.margin=unit(c(2,2,5,2),'mm'))

## function to make a table variants based on selected nucleotide length bins
snpfreqtable <- function (chr_len=chr_len, bin_len=bin_len, hm=hm, ht=ht){
  # chr_len = length of the chromosome
	# bin_len = length nucleotide bins used for poolig variants
	# hm = homozygous variant positions and ht = heterozygous variant positions

	breaks <- bin_len*c(1:ceiling(chr_len/bin_len))
	freqtable <- data.frame(t(rep(NA,3)))
	names(freqtable) <- c("position", "homozy", "heterozy")
	for (i in 1:length(breaks)) {
		lowlimit = breaks[i] - (bin_len - 1)
		a = breaks[i]
		b = 0.1
		c = 0.1

		for (j in 1:length(hm$V1)) {
			if (hm$V1[j] >= lowlimit && hm$V1[j] <= breaks[i]) {
				b = b + 1
			}
		}

		for (k in 1:length(ht$V1)) {
			if (ht$V1[k] >= lowlimit && ht$V1[k] <= breaks[i]) {
				c = c + 1
			}
		}
		freqtable[i,] <- c(a, b, c)
	}
	freqtable$ratio <- freqtable$homozy / freqtable$heterozy
	return(freqtable)
}

## set working directory
setwd("/Users/rallapag/git-hub-repos/shyamrallapalli/mutations_hts_noref/002_snps_in_assembled_genome/variant_data/BCF2_chromosome3")

```

...     

...			

#### Parent filtered [BCF2](https://github.com/shyamrallapalli/SNP_distribution_method/tree/master/Reads/BCF2/BCF2_chromosome3/Interesting_3) chromosome3 data

```{r parent_filtered, echo=FALSE, fig.width=12, fig.height=6}
hm_parent <- read.table("hm_parent_filter.txt")
ht_parent <- read.table("ht_parent_filter.txt")
chr3len <- 23459830 # arabidopsis chromosome3 length

parent_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_parent, ht=ht_parent)
ggplot(data=parent_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="parent fileterd variants")

"bur0_assembled_chr_length.txt"
"c24_assembled_chr_length.txt"
"kro0_assembled_chr_length.txt"
"ler_assembled_chr_length.txt"
"pacbio_ler0_assembled_chr_length.txt"

```

...			

...			

#### Parent and centromere filtered [BCF2] chromosome3 data

```{r parent_centro_filter, echo=FALSE, fig.width=12, fig.height=6}
hmp_nocen <- read.table("hm_parent_filter_nocen.txt")
htp_nocen <- read.table("ht_parent_filter_nocen.txt")

parent_nocendf <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hmp_nocen, ht=htp_nocen)
ggplot(data=parent_nocendf, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="parent and centromere fileterd variants")

```

...			

...  		

#### Bur-0 assembled chromosome3 and BCF2 variant data

```{r bur-0, echo=FALSE, fig.width=12, fig.height=6}
hm_bur0 <- read.table("vars_bur_assembly_hm_parent_filter.txt")
ht_bur0 <- read.table("vars_bur_assembly_ht_parent_filter.txt")

bur0_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_bur0, ht=ht_bur0)
ggplot(data=bur0_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="BCF2 variant data on Bur-0 assembled chromosome 3")

```

...			


...  		

#### C24 assembled chromosome3 and BCF2 variant data

```{r c24, echo=FALSE, fig.width=12, fig.height=6}
hm_c24 <- read.table("vars_c24_assembly_hm_parent_filter.txt")
ht_c24 <- read.table("vars_c24_assembly_ht_parent_filter.txt")

c24_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_c24, ht=ht_c24)
ggplot(data=c24_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="BCF2 variant data on C24 assembled chromosome 3")

```

...			


...    	

#### Kro-0 assembled chromosome3 and BCF2 variant data

```{r kro0, echo=FALSE, fig.width=12, fig.height=6}
hm_kro0 <- read.table("vars_kro0_assembly_hm_parent_filter.txt")
ht_kro0 <- read.table("vars_kro0_assembly_ht_parent_filter.txt")

kro0_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_kro0, ht=ht_kro0)
ggplot(data=kro0_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="BCF2 variant data on Kro-0 assembled chromosome 3")

```

...			


...      

#### Ler-1 assembled chromosome3 and BCF2 variant data

```{r ler-1, echo=FALSE, fig.width=12, fig.height=6}
hm_ler1 <- read.table("vars_ler_assembly_hm.txt")
ht_ler1 <- read.table("vars_ler_assembly_ht_parent_filter.txt")

ler1_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_ler1, ht=ht_ler1)
ggplot(data=ler1_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="BCF2 variant data on Ler-1 assembled chromosome 3")

```

...			


...      

#### Ler-1 pacbio assembled chromosome3 and BCF2 variant data

```{r pacler1, echo=FALSE, fig.width=12, fig.height=6}
hm_pacler1 <- read.table("vars_pacbio_ler0_assembly_hm_parent_filter.txt")
ht_pacler1 <- read.table("vars_pacbio_ler0_assembly_ht_parent_filter.txt")

pacler_df <- snpfreqtable(chr_len = chr3len, bin_len = 1000000, hm=hm_pacler1, ht=ht_pacler1)
ggplot(data=pacler_df, aes(x=position)) + geom_line(aes(y=ratio/sum(ratio)), colour="red") + geom_line(aes(y=homozy/sum(homozy)), colour ="blue") + geom_line(aes(y=heterozy/sum(heterozy)), colour="black") + scale_y_sqrt() + mytheme + labs(y=NULL, main="BCF2 variant data on Ler-1 pacbio assembled chromosome 3")

```

...  		

